%Colton Grainger copied the old syllabus into this file on 2019-04-04.
\documentclass[12pt]{amsart}
\usepackage{geometry}
\geometry{margin=1.25in}
\usepackage{parskip}
\renewcommand{\abstractname}{Note}
\setcounter{secnumdepth}{0}


\title{Analysis Prelim Syllabus}
%\title{Real Analysis Prelim Syllabus}
\author{Department of Mathematics\\ University of Colorado}

\begin{document}

\maketitle

\begin{abstract}
The analysis prelim will be based on material related to the topics
%The real analysis prelim will be based on material related to the topics
listed below. This list is not meant to be exhaustive, but is intended
to be a guide to subjects to be studied thoroughly.
\end{abstract}

\subsection{Metric Spaces.}

Completeness, compactness, connectedness, Ascoli-­Arzela Theorem,
Stone--Weierstrass Theorem.

\subsection{Measure and Integration}

Integration theory on general measure spaces including Lebesgue integral
and Lebesgue-­Stieltjes integral on the line, Lusin's Theorem, Egoroff's
Theorem, Fatou's Lemma, the Monotone and Dominated Convergence Theorems,
convergence in measure, dense subspaces of \(L^1\) (e.g., simple
functions, continuous functions with compact support, etc.)
Radon-­Nikodym Theorem, Tonelli and Fubini Theorems.

\subsection{\(L^p\) spaces}

Hölder and Minkowski Inequalities, Riesz Representation Theorem for
\(L^p\) spaces, completeness of \(L^p\), dense subspaces of \(L^p\).

\subsection{Hilbert spaces}
%this section used to be "item D" 

Bases, \(L^2\) convergence of Fourier series.
%needs more?

\subsection{Differentiation}

Differentiation of monotone functions, differentiation of an indefinite
integral, functions of bounded variation, absolute continuity,
Fundamental Theorem of Lebesgue Calculus, Lebesgue points.

\section{References}

G. B. Folland, \emph{Real Analysis.} Second edition. John Wiley \& Sons,
Inc., 1999.

T.M. Apostol, \emph{Mathematical Analysis}. Second edition.
Addison-Wesley, 1974.

H. L. Royden, \emph{Real analysis}. Third edition. Macmillan Publishing
Company, 1988.

W. Rudin, \emph{Real and Complex Analysis}. Third edition. McGraw-Hill
Book Co., 1987.


\end{document}
